
## Introduction

So, you want to learn some R. Well, strap on and strap in.

### Our psychophysical data

We usually use repeated measures. What does typical data look like? Let's say we have data of 3 participants, each have 5 trials on which they responded
yes or no (1 or 0).

```{r Load table of data, include=FALSE}
  npp = 3
  ntrials = 5
  ntrialstot = npp * ntrials
  
  Trial = rep(1:ntrials, npp)
  Participant = c(rep(1, ntrials), rep(2, ntrials), rep(3, ntrials))
  Response = round(runif(ntrialstot, 0, 1.4))
  df = data.frame("Participant" = Participant, "Trial" = Trial, "Response" = Response)
```

```{r Show table of data, echo=FALSE, fig.width=1}
  library(knitr)
  kable(df, format = 'html')
  
```

### Generated data

In this case we will generate some data.

### Loading your data

To load our data we usually want to use the read.table or read.csv functions.
Be aware that if you copy-paste the location of the document (i.e. "C:\Users\Documents...") that you have to invert the slashes (from '\' to '/') at least on a 
windows computer. For example, to load up a file @ C:\Users\Documents\data.csv and save it in a variable called 'df' we would run the following code.

Again, the following DOESN'T work.
```{r readtable, eval = FALSE}
    df = read.csv("C:\Users\Documents\data.csv")
```

This DOES work.
```{r readtable2, eval = FALSE}
    df = read.csv("C:/Users/Documents/data.csv")
```

## Going beyond basic R

### Installing packages

To install packages use the following command.
```{r Install packages, eval=FALSE}
    install.packages("lme4")
```

To then load the package, and to be actually able to use the functions, use the following command.
```{r Load package, eval=FALSE}
    library("lme4")
```


A quick way to install a couple of packages in one go is to make a list of packages you want to install, and use a for loop to install/activate them.
```{r Simple for loop for packages, eval=FALSE}
    listOfPackages = c("lme4", "ggplot2")
    for (package in listofPackages){
      install.packages(package)
      library(package)
    }

```


