
## Introduction

So, you want to learn some R. Well, strap on and strap in.

### Our psychophysical data

We usually use repeated measures. What does typical data look like?

### Generated data

In this case we will generate some data.

### Loading your data

To load our data we usually want to use the read.table or read.csv functions.
Be aware that if you copy-paste the location of the document (i.e. "C:\Users\Documents...") that you have to invert the slashes (from '\' to '/') at least on a 
windows computer.

```{r}
    plot(cars)

```

## Going beyond basic R

### Installing packages

To install packages use the following command.
```{r}
    install.packages("lme4")
```
To then load the package and to be actually able to use the functions, use the following command.
```{r}
    library("lme4")
```
A quick way to install a couple of packages in one go is to make a list of packages you want to install, and use a for loop to install/activate them.

```{r}
    listOfPackages = c("lme4", "ggplot2")
    for (package in listofPackages){
      install.packages(package)
      library(package)
    }

```


